---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# themes360info
Helpers for creating graphics with ggplot2 that align with 360info style guides

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

# Installation

First, download and install either the [Libre Franklin fonts](https://fonts.google.com/specimen/Libre+Franklin) or the [ITC Franklin Gothic fonts](https://www.myfonts.com/fonts/itc/franklin-gothic/) and install them.

Then install the package with:

```r
remotes::install_github("360-info/themes360info")
```

## Use

To create plots in our style:

* Add `themes360info::theme_360` to your ggplot2 plot;
* Add our fonts to other elements, like annotations or additional theme customisations (see the ["Working with fonts" article](articles/articles/working-with-fonts.html));
* Save the plot, adding a footer with the 360 logo, using `themes360info::save_plot`

## Issues

Please feel free to [get in touch](https://github.com/360-info/themes360info/issues/new) if you have problems with the package or would like to suggest new features.

## Next features

* 360 colour paletter helpers
* Annotation textboxes with `ggtext`:

```{r textboxdemo}
# not working yet!
# p2 <- p1 +
#   textbox_360("blue",
#     x = Inf, y = Inf, hjust = "inward", vjust = "inward", halign = 1,
#     label = "**THIS IS A PATTERN**<br>As one measure gets bigger, the other gets smaller."
#   )
# ggsave("test2.png", p2)
```
