---
title: "Making graphics in the 360info style"
author: "James Goldie, 360info"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Who's this guide for?

This guide is intended for 360info staff who're either:

1. Data or Multimedia staff who need to make common kinds of graphics quickly; or
2. Editors who are learning to make graphics themselves and who are also 

::: {.alert .alert-warning}
**This guide presumes some knowledge!**

If you haven't used R before, I recommend starting your journey with the amazing [RYouWithMe](https://rladiessydney.org/courses/ryouwithme), written by Jen Richmond and Danielle Navarro.

It's designed for students and researchers with no experience of data science and takes you through the process of bringing a simple dataset into R, asking and answering some questions, and making some graphics with `ggplot2`, the graphics system we'll be using.

You should be ready to jump into this vignette once you've run throug that, but if you're still looking to get better with R, try [R for Data Science](https://r4ds.had.co.nz). It's a much more thorough introduction to R, but it's still designed with beginners in mind!
:::


```{r setup}
library(themes360info)
```

## 360info graphics essentials

* `theme_360`
* Fonts in geoms
* Adding a logo and saving to disk
  - Sizing plots
  - Formats: PNG, SVG

## 