---
title: "Working with fonts"
author: "James Goldie, 360info"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "70%",
  fig.align = "center"
)
```

We bundle [Public Sans](https://fonts.google.com/specimen/Public+Sans) with the package. The `themes360info` package takes care of using them when you make plots.

For example, here's a very simple ggplot in the default style:

```{r demoplotregular}
library(ggplot2)
library(themes360info)

p1 <-
  ggplot(diamonds) +
  aes(carat, price) +
  geom_point() +
  labs(
    title = "BIG TITLE",
    subtitle = "More nuanced message here",
    caption = "**SOURCE:** some important place")

test_path <- knitr::fig_path(".png")
ggsave(test_path)
knitr::include_graphics(test_path)
```

Simply adding `theme_360` to this plot will convert a regular ggplot into one that uses our fonts for the title, subtitle, caption and axes:

```{r demoplot360}
p2 <- p1 + theme_360()

test_path <- knitr::fig_path(".png")
save_360plot(p2, test_path, shape = "square", retina = 2)
knitr::include_graphics(test_path)
```

(You might also notice that the caption now interprets the asterisks as **bold text**. Some limited [Markdown](https://www.markdownguide.org/basic-syntax/#emphasis) or HTML formatting is available in the caption for this purpose! You should also use `<br>` instead of `\n` to break a long caption or subtitle across two or more lines.)

## Styling annotations and labels

Although `theme_360` gets us a long way to a 360-styled plot, the fonts aren't added automatically for all elements. For example, see this plot, where we add an annotation:

```{r labeldemobroken}
p3 <-
  p1 +
  annotate("text",
    label = "Here's an additional comment.",
    x = 5, y = 2500,
    hjust = "inward", vjust = "inward") +
  theme_360()

test_path <- knitr::fig_path(".png")
save_360plot(p3, test_path, shape = "square", retina = 2)
knitr::include_graphics(test_path)
```

The other elements are styled correctly, but not the annotation.

Several elements require us to manually specify the font:

* One-off text annotations using `ggplot2::annotate_360` or its variants
* Labels for our data using `ggplot2::geom_text` or `ggplot2::geom_label`
* Additional theme customisations beyond `theme_360`, using `ggplot2::theme`

## Using 360 fonts in other parts of the plot

Because we occasionally update our branding, the `themes360info` package uses virtual fonts that work regardless of which actual font we've bundled with the package. Use:

* `"Headline 360info"`: used for the plot title or _very large_ (essentially title size) annotations
* "Body 360info": used for everything else. This has regular and bold weights (the bold being equivalent to the subhead font) for when you need to mix regular and bold content in an annotation.
  - Since this is the default font, you can generally get away with just specifying the weight for most theme elements, rather than needing to remember the name.

Note that `"Headline 360info"` is typically used in uppercase only, but the package doesn't do that for you. Wrap your plot `title` and `subtitle` in `toupper` to transform them to uppercase (OR JUST TYPE THEM LOUDLY).

Let's try it out:

```{r labeldemofixed}

p4 <-
  p1 +
  annotate_360_glasslight(
    label = "Notice anything different?",
    x = 5, y = 2500,
    hjust = "inward", vjust = "inward") +
  theme_360()

test_path <- knitr::fig_path(".png")
save_360plot(p4, test_path, shape = "square", retina = 2)
knitr::include_graphics(test_path)
```

Because these annotations are also powered by `ggtext`, we can mix and match bold and regular text, as we can in the caption, or even change colours part way through.